When are Fuzzy Extractors Possible?

### 2014-10-03 trunk/info-bounds/FuzzyExtPossibility.tex
editing everything after intro

The same problem occurs in the interactive setting, in which the secret channel used for transmitting the bits between two users is noisy and/or leaky~\cite{Wyner75}. Bennet, Brassard, and Robert~\cite{bennett1988privacy} identify two fundamental tasks.  The first, called information-reconciliation, removes the noise without leaking significant information. The second, known as privacy amplification, converts the high entropy secret to a uniform random value.  In this work, we consider the non-interactive version of these problems, in which these tasks are performed with a single message.

@@

\paragraph{Fuzzy Min-entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within a ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_w' \Pr[W\in B_t(w')]$.

Super-logarithmic fuzzy min-entropy  is necessary for nontrivial key extraction~(\lemref{lem:fuzz necessary}). 
Most known fuzzy extractors obtain security proportional to $\Hoo(W)-\log |B_t(\cdot)|$.  \lnote{know they don't -- that's better than they achieve, because coding is not that good}
Observe that $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W) \le \Hoo(W)$.  However, the lower bound is too imprecise (sometimes even negative) for practical settings.  As an example, iris scans~\cite[Section 5]{blanton2009biometric} appear to have significant $\Hfuzz(W)$ but the value $\Hoo(W) -\log |B_t|<0$.\footnote{Iris scans appear to have $\Hfuzz$ because all iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing} and thus $\Hfuzz(W) = \Hoo(W)$.}
We ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?}

\paragraph{Characterization  for Distribution-aware Extractability}
We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.  While our constructions are not polynomial-time (they are dependent on knowing the complete distribution of $W$), we discuss  how in related settings polynomial-time constructions that provide only computational (rather information-theoretic) security are possible in \secref{sec:related settings}.

@@

\paragraph{A New Impossibility Result}

However, fuzzy extractor designs are typically not tailored to a particular source, but rather for a family sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors). Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary may have some side information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.

We showthat this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
Specifically, we show a family of distributions $\mathcal{W}$ such that no fuzzy extractor can be secure for most elements of $\mathcal{W}$.  We emphasize that each distribution $W\in \mathcal{W}$ has fuzzy min-entropy and all points in $W$ are distance at least $t$ apart. \lnote{can we say this a bit better and more precisely, by relating $\Hfuzz$ and $\Hoo$?}  For comparison with the previous setting we call this type of fuzzy extractor \emph{distribution-oblivious}.

\anote{Suggested title: "Results on Information Reconciliation (Secure Sketches)"}

\paragraph{Results on Information Reconciliation}
Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.  The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.  We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.

A secure sketch performs non-interactive information-reconciliation.  We show comparable results for secure sketches.  Secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}), and yet there is a family of distributions for which no secure sketch in possible~(\thref{thm:imposs sketch}). Our negative results for secure sketches have significantly better parameters than our negative result for fuzzy extractors.

\begin{table}
\begin{center}
\begin{tabular}{c | c | c }
 & Distribution-Aware & Distribution-Oblivious\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}
\paragraph{Our approach} In the distribution-aware setting we begin by constructing a secure sketch on distributions where all points have roughly the same probability.  We call this type of distribution nearly flat.  The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.  Thus, for nearly flat distributions fuzzy min-entropy is maintained if a sketch disambiguates any point in the distribution within distance $t$.  We use universal hashing to disambiguate points.

@@

\subsection{Sufficiency of $\Hfuzz$ in related settings}
\label{sec:related settings}
We have evidence that fuzzy min-entropy is a sufficient condition in several related settings.  
%We first consider the interactive setting.  
First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.  In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.  We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.  Our negative result implies that $W|p$ cannot have pseudoentropy~(see \secref{sec:feas comp sec sketch} for discussion).

@@

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:distribution aware}, we describe the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.  In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.

@@

In this section, we define of fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with changes.  First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  In the \emph{distribution-aware} setting, the algorithms work for a single distribution $W$.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

@@

\paragraph{Distribution-aware setting}
We separate between two types of fuzzy extractors and secure sketches.  Because we rarely have complete descriptions of a physical probability distribution the standard definition requires a fuzzy extractor/secure sketch to work for a family of distributions $\mathcal{W}$.  We call this type of algorithm \emph{distribution-oblivious}.  We define a new type of algorithm called distribution-aware that is allowed to know the precise distribution to be supported.  We provide a definition for secure sketches~(extendible to fuzzy extractors):

@@

\section{Distribution-Aware  Sketches}
\label{sec:distribution aware}
In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors using \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
We first consider distributions where points are far apart, distributions where all points have the same probability, and finally arbitrary distributions.

@@

\subsection{Well-Spread Distributions}
\bnote{can remove this section if we need space}
We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.  Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.  Error-correction is ``easy'' when all points of $W$ are far apart.  Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points.  %Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).  However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.  
We begin by defining a well-spread distribution.

\begin{definition}
A distribution $W$ is called \emph{$t_{cor}$-well spread} if for all $w, x\in W, \dis(w, x)\ge t_{cor}$.
\end{definition}
Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has super-logarithmic min-entropy).  Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.\footnote{This result is intuitive.  However, our negative results for the distribution-oblivious setting will be for families of well-spread distributions.  This result illustrates how different the distribution-aware and distribution-oblivious settings are.}
\begin{lemma}
\label{lem:nosketchwellspread}
Let $W$ be a $t_{cor}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, W, m, \lfloor( t_{cor}-1)/2\rfloor)$-secure sketch with no error that works for $W$.  In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.  \rec is efficient if there exists efficient decoding for the points in $W$.  By \lemref{lem:fuzzy ext construction} there also exists a $(\mathcal{M}, W,m -2\log 1/\epsilon, \lfloor (t_{cor}-1)/2\rfloor, \epsilon)$-fuzzy extractor with no error.
\end{lemma}  
\begin{proof}
It suffices to show that for any $w'$ there exists a unique $w\in W$ such that $\dis (w, w')\le \lfloor (t_{cor}-1)/2\rfloor$.  Since $W$ is $t_{cor}$-well spread, for all $w_0, w_1 \in W, \dis (w_0, w_1)\ge t_{cor}$.  Then by the triangle inequality,
\[
t_{cor}\ge \dis(w_0, w_1) \ge \dis(w_0, w') + \dis(w', w_1).\]
This is only true if at least one of $\dis(w_0, w')$ or $\dis(w', w_1)$ is greater than $\lfloor (t_{cor}-1)/2\rfloor$.
\end{proof}

\subsection{Secure Sketches for Flat distributions}
We showed it is easy to produce secure sketch for well-spread distributions in the distribution aware setting.
%\lemref{lem:nosketchwellspread} showed that if a fuzzy extractor~(resp. secure sketch) is built for a particular well-spread distribution, it is not necessary to write down information-reconciliation information.  
In this section, we consider distributions with multiple points in each ball where points have the same probability.

@@

Recall that fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.  Fuzzy min-entropy is total weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).  For flat distributions, this is proportional to the largest number of points in any ball.  More precisely, 
\begin{align*}
\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \\
&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \\
&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)
\end{align*}
For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  For any scheme, the adversary's success probability is 
\begin{align}
\Hfuzz(W) = \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
\end{align}

@@

For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). The achievable security is proportional to the starting entropy minus the largest number of points in any ball.   Thus, for flat distributions, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ based on $\Hfuzz(W)$).

\subsection{Secure sketches for all distributions with fuzzy min-entropy}
The hashing approach used for flat~(\consref{cons:universal hash}) does not work for arbitrary sources.  The reason is that some balls may have significantly more points but low overall probability.  Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be well-spread balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.  Then the hashing algorithm writes down $\Hoo(W)$ bits in the case when $W$ lands in $B_1$.  However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash completely reveals the point.

@@

As mentioned, the main obstacle in the arbitrary setting is distinguishing between a setting where a ball has a few high probability points and a large number of low probability points.
We address this by describing the probability of the point $w_0\in W$ seen in sketch.  Then the hash is applied only considering the maximum weight of the ball containing points of similar probability.  We can think of this construction as dividing the distribution $W$ into probability levels, and each component level is nearly flat.  As long as levels are large enough, they do not reveal too much information about the stored point $W$.  Naturally, there is a tradeoff between the number of levels and how useful the level information is to both the \rep algorithm and the adversary.

>>>>

The same problem occurs in the interactive setting, in which the secret channel used for transmitting the bits between two users is noisy and/or leaky~\cite{wyner1975wire}. Bennet, Brassard, and Robert~\cite{bennett1988privacy} identify two fundamental tasks.  The first, called information-reconciliation, removes the noise without leaking significant information. The second, known as privacy amplification, converts the high entropy secret to a uniform random value.  In this work, we consider the non-interactive version of these problems, in which these tasks are performed with a single message.

@@

\paragraph{Fuzzy Min-entropy}
We introduce a new entropy notion that precisely measures how hard it is for the adversary to guess a value within distance $t$ of the original reading $w$, thus subverting security of $\key$ by running $\rep$. Suppose $w$ is sampled from a distribution $W$.   To have the maximum chance that $w'$ is within distance $t$ of $w$, the adversary would want to maximize the total probability mass of $W$ within a ball $B_t(w')$ of radius $t$ around $w'$.
We  therefore define \emph{fuzzy min-entropy} $\Hfuzz(W) \eqdef -\log \max_{w'} \Pr[W\in B_t(w')]$.

Super-logarithmic fuzzy min-entropy  is necessary for nontrivial key extraction~(\lemref{lem:fuzz necessary}). 
Most known fuzzy extractors obtain security proportional to $\Hoo(W)-\log |B_t(\cdot)|$.  \lnote{know they don't -- that's better than they achieve, because coding is not that good} \bnote{I agree but I didn't know how to introduce this value otherwise.  Seems like we need a reason to talk about $\Hoo(W) - \log |B_t|$.}
Observe that $\Hoo(W)-\log |B_t(\cdot)| \le \Hfuzz(W) \le \Hoo(W)$.  However, the lower bound is too imprecise (sometimes even negative) for practical settings.  As an example, iris scans~\cite[Section 5]{blanton2009biometric} appear to have significant $\Hfuzz(W)$ but the value $\Hoo(W) -\log |B_t|<0$.\footnote{Iris scans appear to have $\Hfuzz$ because all iris scans for different people appear to be well-spread in the metric space~\cite{daugman2006probing} and thus $\Hfuzz(W) = \Hoo(W)$.}
We ask: \emph{is fuzzy min-entropy sufficient for fuzzy extraction?}

\paragraph{Characterization  for Distribution-aware Extractability}
We show that for every source $W$ with super-logarithmic $\Hfuzz(W)$, it is possible to construct a fuzzy extractor with a super-logarithmic length $\key$ (\corref{cor:extension to fuzz ext}). We thus show that $\Hfuzz(W)$ is a necessary and sufficient condition for building a fuzzy extractor for a distribution $W$.  While our constructions are not polynomial-time (they are dependent on knowing the complete distribution of $W$), we discuss  how in related settings polynomial-time constructions that provide only computational (rather than information-theoretic) security are possible in \secref{sec:related settings}.

@@

\paragraph{Impossibility of Fuzzy Extractors for Families of Distributions}
Typically, fuzzy extractor designs cannot be tailored to a particular source, rather they provide security for a family of sources (for example, all sources of min-entropy at least $k$ with at most $t$ errors). Making minimal assumptions about the distribution $W$ is desirable for two reasons: 1) for high entropy distributions, only a small part of the distribution has been observed 2) the adversary know some additional information about the distribution $W$ and thus the adversaries view of the distribution is different than that of the algorithm designer.

We show that this extra adversarial knowledge can be devastating  (\thref{thm:imposs fuzz ext}). 
Specifically, we show a family of distributions $\mathcal{W}$ such that no fuzzy extractor can be secure for most elements of $\mathcal{W}$.  We emphasize that each distribution $W\in \mathcal{W}$ has fuzzy min-entropy and all points in $W$ are distance at least $t$ apart. \lnote{can we say this a bit better and more precisely, by relating $\Hfuzz$ and $\Hoo$?}  For comparison with the previous setting we call this type of fuzzy extractor \emph{distribution-oblivious}.

\paragraph{Results on Information Reconciliation (Secure Sketches)}
Traditionally, fuzzy extractors use a secure sketch to perform information reconciliation~(mapping $w'$ back to $w$) and a randomness extractor~\cite{nisan1993randomness} to transform $w$ into a uniform key.  The security losses incurred in information-reconciliation dominate for most sources.\footnote{The task of privacy amplification is well-understand.  We have bounds on the length of a key extractible from a source with entropy and extractors that match this bound.}  A secure sketch is a pair of algorithms: $\sketch$ takes $w$ and produces a non secret value $ss$, $\rec$ takes $ss$ and a nearby value $w'$ and outputs the original reading $w$.

A secure sketch performs non-interactive information-reconciliation.  We show comparable results for secure sketches.  Secure sketches are possible if the distribution $W$ is precisely known~(\thref{cons:leveling}), and yet there is a family of distributions for which no secure sketch in possible~(\thref{thm:imposs sketch}). We build our distribution-aware fuzzy extractor by applying a randomness extractor to our distribution-aware secure sketch.  Our negative results for secure sketches have significantly better parameters than our negative result for fuzzy extractors.

\begin{table}
\begin{center}
\begin{tabular}{c  l l }
 & Distribution-Aware & Distribution-Oblivious\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & No~(\thref{thm:imposs fuzz ext}) 
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient to extract a super-logarithmic length key?  Results are information-theoretic.}
\label{tab:main results}
\end{table}
\bnote{is this table doing anything or just getting in the way?  provides a quick glance to results}

\paragraph{Techniques} In the distribution-aware setting, we construct a secure sketch for an arbitrary distribution $W$.  We begin with distributions where all points have roughly the same probability.  We call this type of distribution nearly flat.  Consider some subsequent reading $w'$. To achieve correctness, the sketch algorithm must describe which point $w\in W$ within distance $t$ of $w'$ was sketched.  The fuzzy min-entropy of nearly flat distributions is determined by the ball with the greatest number of points.   Thus, for nearly flat distributions, security is maintained if we always provide enough information to disambiguate the ball with the greatest number of points.  We use universal hashing to disambiguate points.

For an arbitrary distribution, we cannot afford to disambiguate points in the ball with the greatest number of points.  We solve this problem by splitting the arbitrary distribution into a number of nearly flat distributions we call levels.  We then write down the level of the original reading $w$ and apply the above construction considering only points in that level.  We call this construction \emph{leveled hashing}.%: it separates the distribution $W$ into levels that are nearly flat and then hashes to disambiguate the most likely ball at that level.

Our negative results are in the distribution-oblivious setting.  A fuzzy extractor $(\gen, \rep)$ receives a point $w\leftarrow W$, the goal of $\gen$ is to produce a string $p$ that does not reveal much about $w$~(or the derived key).  However, $\gen$ does not see the distribution $W$, only the sample $w$.  This creates an asymmetry, the adversary knows $W$, while $\gen$ only knows the sample $w$ and the family of distributions $\mathcal{W}$.  We construct a family of distributions $\mathcal{W}$ where having seen $w$, the remainder of the support is uniform.  Our family $\mathcal{W}$ is the set of affine lines.  For any distribution, the nonsecret value $p$ partitions the metric space into regions that produce a consistent value under $\rep$.  For each of these regions, the adversary knows that possible $w$ lie far from the boundary of the region.  However, in the Hamming space the majority of points lie near the boundary.  Since the fuzzy extractor does not know the rest of $W$, it places most points of $W$ near a boundary.  This means that $W|p$ is small.  This is enough to break security.

 The partition induced the public value is different for fuzzy extractors and secure sketches, leading to different theorem statements and proofs.  
The result for secure sketches is strong, it only requires the secure sketch to correct a constant, $t=4$, errors and allows $\rec$ to be wrong almost a quarter of the time.  The result for fuzzy extractors is more delicate, it requires a metric space where for any set of points~(of a bounded size), most points are close to a point outside the set.  Our negative result for fuzzy extractors is in the binary Hamming space and this property is obtained by combining the isoparametric inequality~\cite{harper1966optimal} and Hoeffding's inequality~\cite{hoeffding1963probability}.

Fuzzy extractors for arbitrary distributions are known in metric spaces where the boundary of a set does not consistent the majority of its area.\bnote{cite cite cite!!!}

@@

\subsection{Sufficiency of $\Hfuzz$ in related settings}
\label{sec:related settings}
We have evidence that fuzzy min-entropy is sufficient in settings related to information-theoretic fuzzy extractors.  
%We first consider the interactive setting.  
First, an alternate definition fuzzy extractors and secure sketches may provide computational security instead of information-theoretical security~\cite{fuller2013computational}.  In this setting, under the strong assumption of semantically-secure multilinear maps, fuzzy extractors and secure sketches can be constructed for any distribution $W$~\cite{BitanskyCKP14}.  We note that the secure sketch of~\cite{BitanskyCKP14} provides computational unpredictability of $W |p$.  Our negative result that implies that $W|p$ cannot have pseudoentropy~(discussion in \secref{sec:feas comp sec sketch}).

@@

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:distribution aware}, we construct a distribution-aware fuzzy extractor for all distributions with fuzzy min-entropy.  In Sections~\ref{sec:dist oblivious} and~\ref{sec:imposs fuzz ext} we provide negative results for the distribution-oblivious secure sketches and fuzzy extractors respectively.

@@

In this section, we define of fuzzy extractors and secure sketches.  Definitions and lemmas are drawn from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with changes.  First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Second, in the \emph{distribution-oblivious} setting we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.
%\footnote{Our negative results rule out a family that is a subset of all distributions with given min-entropy and thus rules out all distributions of a given entropy.}  
This is a generalization of the definition of Dodis et al. which require a fuzzy extractor to work for all distributions of a particular entropy.  We cover the distribution-aware setting in \secref{sec:distribution aware}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$. \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$. \rep takes $w'\in\mathcal{M}$ and $p\in\{0,1\}^*$ as inputs.   $(\gen, \rep)$ have the following properties:
\begin{enumerate}
\item \emph{Correctness:} if $\dis(w, w')\leq t$ and $(r, p)\leftarrow \gen(w)$, then $\Pr[\rep( w', p) = r] \geq 1-\delta$.
\item \emph{Security:} for any distribution $W\in\mathcal{W}$, if $(R,P)\leftarrow\gen (W)$, then $\sd((R,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

@@

@@

\subsection{Distribution-aware setting}
\label{sec:distribution aware}
To show that fuzzy min-entropy is the right notion for fuzzy extractors and secure sketches we show that it is sufficient for fuzzy extraction if the algorithm has complete knowledge of the distribution $W$.  We call this type of algorithm \emph{distribution-aware}.  We provide a definition for secure sketches~(extendible to fuzzy extractors):

\section{Distribution-Aware Information-Reconciliation}
\label{sec:distribution aware}
In this section, we show it is possible to build distribution-aware secure sketches~(and thus fuzzy extractors through \lemref{lem:fuzzy ext construction}) whenever $\Hfuzz(W)= \omega(\log n)$.
We first consider flat distributions and show that hashing maintains fuzzy min-entropy and suffices to disambiguate points.  We then turn to arbitrary distributions.

@@

%\subsection{Well-Spread Distributions}
%\bnote{can remove this section if we need space}
%We call a distribution well-spread if the distance between any two original readings $w_0, w_1$ is large.  Well-spread distributions should be the easiest type of distribution to handle as given a particular $w'$ there is a unique $w$ that could be the original reading.  Error-correction is ``easy'' when all points of $W$ are far apart.  Intuitively, the fuzzy extractor/secure sketch does not need to disambiguate points.  %Indeed for any error-correcting code, a fuzzy extractor can be designed~(where the design of the fuzzy extractor depends on the supported distribution).  However, this intuition becomes more difficult when a fuzzy extractor should work for all well-spread distributions.  
%We begin by defining a well-spread distribution.
%
%\begin{definition}
%A distribution $W$ is called \emph{$t_{cor}$-well spread} if for all $w, x\in W, \dis(w, x)\ge t_{cor}$.
%\end{definition}
%Intuitively, it should be easy to build a fuzzy extractor for well-spread distributions when the desired error-tolerance is less than $t_{cor}/2$~(assuming the distribution has super-logarithmic min-entropy).  Indeed, this is the case when the fuzzy extractor is allowed to depend on $W$.\footnote{This result is intuitive.  However, our negative results for the distribution-oblivious setting will be for families of well-spread distributions.  This result illustrates how different the distribution-aware and distribution-oblivious settings are.}
%\begin{lemma}
%\label{lem:nosketchwellspread}
%Let $W$ be a $t_{cor}$ well-spread distribution with $\Hoo(W)\ge k$ there exists a $(\mathcal{M}, W, m, \lfloor( t_{cor}-1)/2\rfloor)$-secure sketch with no error that works for $W$.  In particular, $\sketch(w) = \perp$, and $\rec(w')$ finds the nearest $w\in W$.  \rec is efficient if there exists efficient decoding for the points in $W$.  By \lemref{lem:fuzzy ext construction} there also exists a $(\mathcal{M}, W,m -2\log 1/\epsilon, \lfloor (t_{cor}-1)/2\rfloor, \epsilon)$-fuzzy extractor with no error.
%\end{lemma}  
%\begin{proof}
%It suffices to show that for any $w'$ there exists a unique $w\in W$ such that $\dis (w, w')\le \lfloor (t_{cor}-1)/2\rfloor$.  Since $W$ is $t_{cor}$-well spread, for all $w_0, w_1 \in W, \dis (w_0, w_1)\ge t_{cor}$.  Then by the triangle inequality,
%\[
%t_{cor}\ge \dis(w_0, w_1) \ge \dis(w_0, w') + \dis(w', w_1).\]
%This is only true if at least one of $\dis(w_0, w')$ or $\dis(w', w_1)$ is greater than $\lfloor (t_{cor}-1)/2\rfloor$.
%\end{proof}

\subsection{Secure Sketches for Flat distributions}
In this section, we consider distributions with multiple points in each ball where points have the same probability.

@@

Fuzzy min-entropy is a lower bound of the adversaries success probability for any scheme.  Fuzzy min-entropy is the weight of the maximum probability ball~(\defref{def:fuzzy min-ent}).  For flat distributions, this is proportional to the largest number of points in any ball.  More precisely, 
\begin{align*}
\Hfuzz(W) &= -\log \left(\max_{w^* \in \mathcal{M}} \left| \{w | w\in W \wedge \dis(w, w^*)\le t\} \right|* \Pr[W=w]\right) \\
&= -\log\left( \max_{w^* \in \mathcal{M}} |\{w | w\in W \wedge \dis(w, w^*)\le t\}| *2^{-\Hoo(W)}\right) \\
&=\Hoo(W) -\log\left( \max_{w^* \in \mathcal{M}}| \{w | w\in W \wedge \dis(w, w^*)\le t\} |\right)
\end{align*}
For notational convenience, we denote the ball with the largest number of points as $B_{t, max}$.  For any scheme, the adversary's success probability is 
\begin{align}
\Hfuzz(W) = \Hoo(W) -\log |B_{t, max}|.\label{eq:fuzz for flat}
\end{align}

@@

For a flat distribution this is within a super-logarithmic factor of optimal~(see Equation~\eqref{eq:fuzz for flat}). Thus, for flat distributions, we can construct a secure sketch that is correct with overwhelming probability while retaining a super-logarithmic amount of entropy~(by choosing $\delta$ based on $\Hfuzz(W)$).

\subsection{Secure sketches for all distributions with fuzzy min-entropy}
The hashing approach just described does not work for arbitrary sources.  The reason is that some balls may have significantly more points but low overall probability.  Let $W$ be a distribution, denote by $B_1$ a ball with $2^{\Hoo(W)}$ points but with probability $\Pr[W\in B_1] =2^{-\Hoo(W)}$ and let $B_2,..., B_{2^{-\Hoo(W)}}$ be balls with one point each with probability $\Pr[W\in B_i] = 2^{-\Hoo(W)}$.  Then the hashing algorithm needs to write down $\Hoo(W)$ bits to achieve correctness.  However, with probability $1-2^{-\Hoo(W)}$ the point $w_0$ lies outside of $B_1$ and the hash completely reveals the point.

@@

As mentioned, the main obstacle in the arbitrary setting is distinguishing between a setting where a ball has a few high probability points and a large number of low probability points.
We address this by describing the probability of the point $w_0\in W$ seen in sketch.  Then the hash is applied only considering the maximum weight of the ball containing points of similar probability.  We can think of this construction as dividing the distribution $W$ into probability levels, and each component level is nearly flat.  As long as levels are large enough, they do not reveal too much information about the stored point $W$.  Naturally, there is a tradeoff between the number of levels and how useful the level information is to both \rep and the adversary.

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$. Let $W$ be a distribution with $\Hfuzz(W)\ge m$.  Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., m+\ell$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal independent hash functions.  We describe $\sketch_W, \rec_W$ as follows: 
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item If $\Pr[W=w] \le 2^{-(m+\ell)}$. Set $p=0,w$.
\item Else
\begin{enumerate}
\item Find $i$ such that $\Pr[W=w]\in L_i$.
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $p =1,  i, F_i(K, w), K$.
\end{enumerate}
\end{enumerate}
\vspace{.4in}
\end{minipage} &
\begin{minipage}{3in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', y)$
\item If $y_0 = 1$, output $y_{1,..., |y|}$.
\item Else
\begin{enumerate}
\item Parse $(i, z, K) = y_{1,..., |y|}$.
\item $W^* = \{w \in W | \dis(w, w')\le t\}$.
\item For $w^*\in W^*$, if $F(K, w^*) = z$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

\begin{theorem}
\label{thm:layered hashing}
Let $W$ be a distribution over $\mathcal{M}$.  Let $\delta>0$ be an function of $n$.  Let $F_i: \mathcal{K}_i \times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions where $|R_i| = (|B_{t, i, max}|-1) /\delta$.  When $\ell = n$ \consref{cons:leveling} is a $(\mathcal{M}, W, \tilde{m}, t)$-secure sketch with error $\delta$ for $\tilde{m} = \Hfuzz(W) - \log n - \log 1/\delta - 3$.

\end{theorem}
We provide a proof in \apref{sec:proof of layered hashing}.  The main idea is to show that an adversary that knows the level of $w$ cannot perform much better than an adversary without this information.
